---
title: "ggradar"
output:
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 300, message = FALSE, warning = FALSE, error = FALSE)
```

`ggradar` allows you to build radar charts with ggplot2. This package is based on [Paul Williamson's](http://rstudio-pubs-static.s3.amazonaws.com/5795_e6e6411731bb4f1b9cc7eb49499c2082.html) code, with new aesthetics and compatibility with ggplot2 2.0.

It was inspired by [d3radaR](http://www.buildingwidgets.com/blog/2015/12/9/week-49-d3radarr), an htmlwidget built by [timelyportfolio](https://github.com/timelyportfolio).

## Install `ggradar`

```{r, eval=FALSE}
devtools::install_github("ricardo-bion/ggradar", 
                          dependencies = TRUE)
```

## Use `ggradar`

```{r, fig.width=15, fig.height=10}
library(ggradar)
library(tidyverse)
library(scales)

mtcars_radar <- mtcars %>% 
  as_tibble(rownames = "group") %>% 
  mutate_at(vars(-group), rescale) %>% 
  tail(4) %>% 
  select(1:10)
```

```{r, echo = FALSE}
knitr::kable(mtcars_radar,format = "markdown") 
```

```{r}
ggradar(mtcars_radar)
```

## Custom fonts

You can also use custom font family in `ggradar`. In the following example, you would like to use Airbnb's font family named 'Circular Air' by first downloading it, installing it in your computer (not shown), and then registering it to R using `extrafont` package.

```{r, eval = TRUE}
# configured to work on a Mac, change directory to Unix or Windows
download.file("https://github.com/ricardo-bion/ggtech/raw/refs/heads/master/Circular%20Air-Light%203.46.45%20PM.ttf", "~/Circular Air-Light 3.46.45 PM.ttf")

library(showtext)

font_add("Circular Air", regular = "~/Circular Air-Light 3.46.45 PM.ttf")

showtext_auto()

```

Following the same procedure as in the previous example, you can then use 'Circular Air' font family in `ggradar` by adjusting `font.radar` argument. The following example shows that `ggradar` is also can be used in pipe `%>%`.

```{r, fig.width=15, fig.height=10}
mtcars %>% 
  as_tibble(rownames = "group") %>% 
  mutate_at(vars(-group), rescale) %>% 
  tail(4) %>% 
  select(1:10) %>% 
  ggradar(font.radar = "Circular Air")
```

## Axis Font Styling

Example of adding observation count in bold to axis labels.

```{r, fig.width=15, fig.height=10}

label_bold = function(row) {
  name <- as.character(row[1])
  n <- as.character(row[2])
  deparse(bquote(bold(.(n))~.(name)))
}

chickwts %>%
  group_by(feed) %>%
  summarise(n=n(), .groups="drop") %>%
  apply(1, label_bold) ->
  axis.labels

chickwts %>%
  group_by(feed) %>%
  summarise(mean_weight=mean(weight), .groups="drop") %>%
  mutate(group = 1) %>%
  mutate_at(vars(-group, -feed), rescale) %>%
  spread(feed, mean_weight) %>%
  ggradar(plot.title = "Chicken Weights by Feed Type", axis.labels = axis.labels, axis.label.parse = TRUE)

```

